True versus apparent shapes of bow shocks

### 2017-12-04 papers/Paper1/sec-conclusions.tex
Finish the simulation section of theory paper
Just need to revisit discussion and abstract now

The resultant inclination-dependent tracks in the planitude--alatude
plane are shown in Figure~\ref{fig:sim-Pi-Lambda}.  These are compared
with measurements\footnote{%
  The shape measurements were performed by converting to contours the
  \SI{60}{\um} images in \citet{Meyer:2017a}'s Fig.~10 and then
  tracing the ridge of minimum radius of curvature of the contours.
  Identical results are found from using the \SI{100}{\um} maps
  instead.  For the \SI{25}{\um} maps, although the same results are
  found for low inclinations, in the maps with
  \(\abs{i} \ge \ang{45}\) in the HD case it becomes impossible to trace
  the limb-brightened rim because it becomes fainter than the emission
  from the true apex of the bow.} %
from post-processed infrared dust continuum maps at \SI{60}{\um}
\citep[\S~4.3 of][]{Meyer:2017a}, shown by open square symbols for
\(i = \ang{30}\), \ang{45}, and \ang{60}.  The agreement between the
two is good.  In particular, the \SI{60}{\um}-derived shapes are
always very close to the tracks derived from the contact discontinuity
shape. Also, the ordering of the three inclinations along the tracks
corresponds to what is predicted, although quantitatively there are
some slight deviations.  This close agreement stems for the fact that
the long-wavelength dust emission from hot-star bow shocks tends to be
dominated by material just outside the contact discontinuity, as
emphasized by \citet{Meyer:2014b}.  Note that there is almost no
difference in the planitude--alatude tracks between the closed and open
extrapolations.  This is because \(\Pi'\) and \(\Lambda'\) only depend on the
portion of \(R(\theta)\) between \(\theta_0\) (eq.~[\ref{eq:thetapar}]) and
\(\theta_{90}\) (eq.~[\ref{eq:th90}]), and these are both smaller than the
\(\theta\) range where extrapolation is necessary, except for in the HD
case at the highest inclinations.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-r0-prime}
  \caption[]{Apparent projected apex distance of simulations.}
  \label{fig:sim-R0-prime}
\end{figure}

Finally, Figure~\ref{fig:sim-R0-prime} shows the inclination
dependence of the projected apex distance, \(R_0'\).  Again, the lines
show the prediction based on the shape of the contact discontinuity,
while the square symbols show the results from the \SI{60}{\um} dust continuum maps.  In addition, triangle symbols show results from H\(\alpha\) optical emission line maps, which are given for \(i = 0\) in

>>>>

The resultant inclination-dependent tracks in the planitude--alatude
plane are shown in Figure~\ref{fig:sim-Pi-Lambda}.  These are compared
with measurements\footnote{%
  The shape measurements were performed by converting to contours the
  \SI{60}{\um} images in \citet{Meyer:2017a}'s Fig.~10 and then
  tracing the ridge of minimum radius of curvature of the contours.
  Identical results are found from using the \SI{100}{\um} maps
  instead.  For the \SI{25}{\um} maps, although the same results are
  found for low inclinations, in the maps with
  \(\abs{i} \ge \ang{45}\) in the HD case it becomes impossible to trace
  the limb-brightened rim because it becomes fainter than the emission
  from the true apex of the bow.} %
from post-processed infrared dust continuum maps at \SI{60}{\um}
\citep[\S~4.3 of][]{Meyer:2017a}, shown by open square symbols for
\(i = \ang{30}\), \ang{45}, and \ang{60}.  The agreement between the
two is good.  In particular, the \SI{60}{\um}-derived shapes are
always very close to the tracks derived from the contact discontinuity
shape. Also, the ordering of the three inclinations along the tracks
corresponds to what is predicted, although quantitatively there are
some slight deviations.  This close agreement stems from the fact,
emphasized by \citet{Meyer:2014b}, that the long-wavelength dust
emission from hot-star bow shocks tends to be dominated by material
just outside the contact discontinuity.  Note that there is almost no
difference in the planitude--alatude tracks between the closed and open
extrapolations.  This is because \(\Pi'\) and \(\Lambda'\) only depend on the
portion of \(R(\theta)\) between \(\theta_0\) (eq.~[\ref{eq:thetapar}]) and
\(\theta_{90}\) (eq.~[\ref{eq:th90}]), and these are both smaller than the
\(\theta\) range where extrapolation is necessary, except for in the HD
case at the highest inclinations.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-r0-prime}
  \caption[]{Apparent projected apex distance of simulations.  Line
    and symbol meanings are as in Figure~\ref{fig:sim-Pi-Lambda}.  In
    addition, triangle symbols at \(\abs{i} = \ang{0}\) denote radius
    measured on H\(\alpha\) optical emission maps.}
  \label{fig:sim-R0-prime}
\end{figure}

Finally, Figure~\ref{fig:sim-R0-prime} shows the inclination
dependence of the projected apex distance, \(R_0'\).  As in the
previous figure, the lines show the prediction based on the shape of
the contact discontinuity, while the square symbols show the results
from the \SI{60}{\um} dust continuum maps.\footnote{%
  There is an apparent error in the spatial scales for the HD
  simulations in Figs.~10 and 11 of \citet{Meyer:2017a}, with the dust
  emission peaks occurring at radii that are clearly too large.  The
  stated apex distance for the contact discontinuity in this
  simulation is \SI{0.69}{pc} from Table~2 of \citet{Meyer:2014b}, and
  the position of the peak in dust column density is \SI{0.70}{pc}
  from Fig.~17a of \citet{Meyer:2014b}.  These are consistent with
  Figs.~3, 4, and 7 of \citet{Meyer:2017a}, but not with Figs.~10 and
  11.  Luckily, the position of the true apex is clearly visible in
  the \SI{25}{\um} maps of Fig.~10 at inclinations of \ang{45} and
  \ang{60}.  The projected separation of the true apex is
  \(R_0 \cos i\), independent of the bow shape, which allows a
  correction factor of \num{0.65} to be found, assuming that the
  on-axis peak in the \SI{25}{\um} emission coincides with the peak in
  dust column density.  This correction has been applied to the blue
  square symbols shown in our Fig.~\ref{fig:sim-R0-prime}.} %
In addition, triangle symbols show results from H\(\alpha\) optical
emission line maps, which are given for \(i = 0\) in Fig.~7 of
\citet{Meyer:2017a}.  Again, the agreement is good between the values
derived from the shape of the contact discontinuity and those derived
from the surface brightness maps. The greatest discrepancy is seen
with the H\(\alpha\) maps and the intermediate inclination dust maps, with
\(R_0'\) being overestimated by a few percent in both cases.  The
differences in behavior between the two simulation are much larger
than this.  The larger true planitude of the MHD simulation means that
the relative increase of \(R_0'\) with \(\abs{i}\) is much stronger
than in the HD simulation for \(\abs{i} < \ang{45}\), as expected from
Figure~\ref{fig:quadric-projection}b.
